Analyzing the Citation Rate of a Scientific Paper Using ML and Graph Algorithms

### 2024-12-18 paper/paper.tex
fill TODOs

\item[1.] Text embeddings. \newline
We tried two different approaches of getting text embeddings:
\begin{enumerate}
\item[a)] Text had been preprocessed using stemmer and stop words removal before applying bag of words vectorization.
\item[b)] Text embeddings with ? \textbf{TODO}
\end{enumerate}

\item[2.] Graph embeddings.\newline
\textbf{TODO}
\end{enumerate}

>>>>

\item[1.] Text embeddings. \newline
We tried two different approaches of getting text embeddings:
\begin{enumerate}
\item[a)] Text had been preprocessed using stemmer and stop words removal before applying bag of words vectorization.
\item[b)] Text embeddings were obtained by averaging the embedding of each word in the abstract using glove-wiki-gigaword model with an embedding size of 50
\end{enumerate}

\item[2.] Graph embeddings.\newline
We used the classic node2vec with default parameters, except that the dimension of the embedding space was 64 (instead of default 128)
\end{enumerate}
